Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-06 submission.tex
changes to section optimized tag set

The most successful tag set modification for each PoS and their results are
seen in Table \ref{respectiveresults}. Nouns benefit by far the most from the
introduction of more fine-grained linguistically motivated distinctions, with
an LAS of 88.81\% and UAS of 91.73\%. We observe that the most promising tag
set modifications for verbs, adjectives, determiners and pronouns all reach LAS
of \textasciitilde 87.30\% and UAS of \textasciitilde 90.40\%. To investigate
the overall effect of these tag set modifications, we tested each of the
improvements in parser accuracy scores from baseline for statistical
significance using Dan Bikel's randomized parsing evaluation comparator
script\footnote{Available as \texttt{compare.pl} at
    \url{http://ilk.uvt.nl/conll/software.html}}, as used in the CoNLL shared
tasks. For the most successful tag set modification for each of the categories
seen in Table \ref{respectiveresults}, the difference in LAS from the original
tag set is statistically significant at significance level 0.05 (\emph{p}-value
< 0.05), as are all differences in UAS, except for verbs with finiteness
(\emph{p}-value 0.15) and pronouns with type and case (\emph{p}-value 0.06).

@@

\paragraph{Final Evaluation}
In Table \ref{finalresults}, we show the results of parsing with the optimized
tag set on the held-out test set, compared to the results obtained with the
original tag set. We see significant improvements from the original tag set on
both the development data and the held-out test data set. The improvement in
LAS on the development data is 1.86 percentage points, while 1.91 percentage
points on the held-out test data. These results indicate that the additional
linguistic information in the tags of our optimized tag set greatly aids
syntactic parsing and that optimizing an existing PoS tag set for a downstream
application can be useful and beneficial.

>>>>

The most successful tag set modification for each PoS and the results from
tagging and parsing with the respective modifications are seen in Table
\ref{respectiveresults}. Nouns benefit by far the most from the introduction of
more fine-grained linguistically motivated distinctions, with an LAS of 88.81\%
and UAS of 91.73\% when distinguishing on type, case and definiteness. We
observe that the most promising tag set modifications for verbs, adjectives,
determiners and pronouns all reach LAS of \textasciitilde 87.30\% and UAS of
\textasciitilde 90.40\%. To investigate the overall effect of these tag set
modifications, we tested each of the improvements in parser accuracy scores
from that of the original tag set for statistical significance using Dan
Bikel's randomized parsing evaluation comparator script\footnote{Available as
    \texttt{compare.pl} at \url{http://ilk.uvt.nl/conll/software.html}}, as
used in the CoNLL shared tasks. For the most successful tag set modification
for each of the categories seen in Table \ref{respectiveresults}, the
difference in LAS from the original tag set is statistically significant at
significance level 0.05 (\emph{p}-value < 0.05), as are all differences in UAS,
except for verbs with finiteness (\emph{p}-value 0.15) and pronouns with type
and case (\emph{p}-value 0.06).

@@

\paragraph{Final Evaluation}
In Table \ref{finalresults}, we show the results of parsing with the optimized
tag set on the held-out test data and the development data, compared to the
results obtained with the original tag set. We see significant improvements
from the original tag set on both the development data and the held-out test
data set. The improvement in LAS on the development data is 1.86 percentage
points, while 1.91 percentage points on the held-out test data. These results
indicate that the additional linguistic information in the tags of our
optimized tag set greatly aids syntactic parsing and that optimizing an
existing PoS tag set for a downstream application can be useful and beneficial.
